---
title: "Day 10 Github Practice"
format: html
editor: visual
execute: 
  echo: false
---

```{r}
#| include: false
#install.packages("lterdatasampler")
library(tidyverse)
library(lterdatasampler)
library(kableExtra)
crabs <- pie_crab
```

## Carapace Plot

The following is a basic scatterplot summarizing fiddler crab carapace lengths by latitude along Atlantic coast.

```{r}
#| fig-cap: "Scatter Plot of Carapace Lengths by Latitude"
ggplot(data = crabs, aes(x = size, y = latitude))+
  geom_point()
```

```{r}
#| include: false
crabs_table <- crabs %>% 
  group_by(site) %>% 
  summarize(mean = round(mean(size), 2), sd = sd(size), sample_size = n())

```

## Summary Table

This table provides summary statistics of fiddler crab carapace lengths, grouped by different sampling sites.

```{r}
crabs_table |> 
  kable(col.names = c("Site",
                      "Mean (mm)",
                      "Standard deviation (mm)",
                      "Sample size")) |> 
  kable_classic()
```

### Citations

Data sourced from:

-   Johnson, D. 2019. Fiddler crab body size in salt marshes from Florida to Massachusetts, USA at PIE and VCR LTER and NOAA NERR sites during summer 2016. ver 1. Environmental Data Initiative. https://doi.org/10.6073/pasta/4c27d2e778d3325d3830a5142e3839bb (Accessed 2021-05-27).

-   Johnson DS, Crowley C, Longmire K, Nelson J, Williams B, Wittyngham S. The fiddler crab, Minuca pugnax, follows Bergmann’s rule. Ecol Evol. 2019;00:1–9. https://doi.org/10.1002/ece3.5883
